### 2025-10-25 thesis/implementation/index.tex
Fix typos

@@

As outlined above the \textsc{OmniSQL} prompt was used as base for
\textsc{Natural}'s prompt together with a . \textsc{Natural} uses more explicit instructions
compared to DAIL-SQL. Key differentiations include the inclusion of similarity
scores to give the model the ability to weight the samples itself and

The prompt emphasizes precision and chain-of-thought reasoning. 
This aims to address common LLM issues with over-generating information or missing
query constraints, as well as the hallucination and accuracy concerns
identified in literature review section where LLMs generate plausible but
incorrect SQL queries.

>>>>

As outlined above the \textsc{OmniSQL} prompt was used as base for
\textsc{Natural}'s prompt together with a code representation prompt.
\textsc{Natural} uses more explicit instructions compared to DAIL-SQL. Key
differentiations include the inclusion of similarity scores to give the model
the ability to weight the samples itself.

This prompt steers the model towards precision and chain-of-thought reasoning. 
It addresses apparent LLM issues like verbosity, over complexity or missing
query constraints, as well as the hallucination and accuracy concerns
identified in literature review section where LLMs generate plausible but
incorrect SQL queries.

@@
